\thispagestyle{empty}
\otherlanguage{english}
\begin{abstract}
%------------------------------------------------------------------------------
% Hintergrund
%------------------------------------------------------------------------------
%\todo{HINTERGRUND}
% Was ist bereits bekannt zum Thema?
%\todo{Was ist bereits bekannt zum Thema?}
The use of batteries in emergency supplies demands a diagnose which estimates
the state of charge and state of health of the battery. The use of a reliable
diagnosis of the battery can ensure the correct operation and optimal use of
batteries' service life.

% Was ist noch unbekannt?
%\todo{Was ist noch unbekannt?}
This study examines which methods are suitable for the diagnosis of
lead-acid batteries used in emergency supplies of elevators.
%
% Was soll die Arbeit untersuchen?
%\todo{Was soll die Arbeit untersuchen?}
It aims to shows how the existing application can be extended with a
method for diagnosis. Hence, a suitable diagnosis system is developed and
implemented. Additionally, the study explores the requirements for the
existing system. Furthermore, it aims to show which modifications and future
work should be addressed for the application, along with a possible
optimization of the diagnosis system.

%------------------------------------------------------------------------------
% Methode 
%------------------------------------------------------------------------------

% Wie war das Vorgehen?
%\todo{Wie war das vorgehen?}
After the exploration of relevant literature, existing methods were classified
and rated. The 2-pulse load test was evaluated as the most suitable method to
be applied. This method was validated through datasheet study of the batteries
and laboratory tests. Based on the analysis of the existing battery management
system, a new diagnosis system was developed. A prototype of this new diagnosis
system has been developed, integrated, and tested in the existing application.

%	
% Welche Mittel sind verwendet worden?
%\todo{Welche Mittel sind verwendet worden?}
%Die Validierung des 2-Puls Lasttest erfolgte mit einem Testsystem, welches das
%Verfahren auf unterschiedliche Batterietypen und mit unterschiedlichen
%Testparametern durchführte.
For the validation the 2-pulse load test was applied within a test installation
and checked with coulomb counting measurements. The test was performed with
different batteries which are used in the existing application. The test of the
implemented prototype was performed on a reduced setup which simulates the use
in the real application with controlled conditions.

%	
% Unter welchen Bedingungen ist untersucht worden?
%\todo{Unter welchen Bedingungen ist untersucht worden?}
%For the validation the 2-pulse load test was applied on different types of
%batteries with multiple samples, different C-rates, multiple temperatures
%and different state of charge of the batteries.
%The validation was performed with

%------------------------------------------------------------------------------
% Ergebnisse
%------------------------------------------------------------------------------
%\todo{ERGEBNISSE}
%The study shows that the 2-pulse load test is suitable for the diagnosis of
%lead-acid batteries in emergency supplies of elevators and a diagnosis system
%can be integrated in the existing applications.

The validation shows that the state of charge and state of health can be
estimated with the 2-pulse load test. The required models and parameters have
been identified. Optimal estimations were observed with the use of specific
battery models. The estimation of the state of health is only reliable for
fully charged batteries and improves with higher load pulses.
%
For the use of the 2-pulse load test a new diagnosis system is introduced and
a prototype integrated in the existing application. The tests of the implemented
prototype shows that the 2-pulse load test can be integrated in the existing
application.

%------------------------------------------------------------------------------
% Schlussfolgerung
%------------------------------------------------------------------------------
%\todo{SCHLUSSFOLGERUNGEN}
There is no standard method for the diagnosis of batteries in emergency
supplies. For these applications the 2-pulse load test is suitable as a
method for the diagnosis of batteries. The test delivers an estimation of the
state of charge and state of health of the battery within less than 8 minutes
and without an interruption of the emergency supply availability. The state of
health estimations reaches an accuracy of at least $\pm 15\%$ at ideal conditions.

% Hauptergebnis
%\todo{Hauptergebnis}

% Zusätzliche Feststellungen
%\todo{Zusätzliche Feststellungen}

% Perspektiven
%\todo{Perspektiven}
The results presented in this study have to be extended with further
investigations. Especially the implemented diagnosis system has to be tested
for long time operation with different batteries. Further, a strategy has to
be developed, how to use the diagnosis and how the estimations are processed.
\end{abstract}
\otherlanguage{ngerman}
