\section{Feedback}

I was not able to fill out the feedback form on moodle, therefore I'm using
this opportunity to give a short feedback to the course.

%\subsection{General feedback}
I got in touch with the script of this module during my bachelors study,
where I had to develop a Phase-Shifted Resonant Converter for a 800W DC/DC supply.
I was impressed of the script, since it covered all the topics I'm interested in. 
This lead me to the decision to start a master study. 

I am very happy with the course! It's just the way I imagined it. Only the pace
of the course is rather high, but the script and sample soulutions enable a good
self-study.

\subsection{Positive}

\begin{itemize}
	\item Lecture starts at a very confortable time (9:45).
	\item \textbf{The script is very good} (organization, layout, depth, details).
	\item The recommended literature\footnote{The Fundamentals of Power
		Electronics by Dragan Maksimovi\'c et. al.} is very good.
		Further, its' terminology, style, and organization is similar
		to the script, hence, it is very easy to work with it.
	\item The exercises are very good. They are focused on the lectures
		contents and can be solved using the script and lecture
		inputs\footnote{Once I was sick and missed the lecture. Due to
		the good script, slides, exercises and solutions I was able
		to do a self-study session on my own.}.
	\item \textbf{The exercise solutions are very good -- I'd like every
		professor to prepare such extensive solutions to the exercises}.
		One can really work on the exercise and check the detailed
		solution. \textbf{It enables a real self-study.} Further, it
		helps avoiding extensive time losses by looking for errors
		in the own solution, in contrast to solutions containing only
		a final numerical value.
	\item The introduction to the Plexim Software PLECS is very
		good and the use in the exercises is really helpful to get
		in touch with it.
\end{itemize}

\subsection{Negative}
\begin{itemize}
	\item Usually there was not much time left to discuss the exercises
		during the lectures (this issue is compensated by the good
		sample solutions).
	\item The attestations had a strong focus on control theory, which is not
		the main focus of this course. I'd rather had the opportunity to
		get more in touch with topics of the course instead.
	\item The lecture pace is rather high regarding the lecture itself and the 
		topic progress (this issue is compensated by the good script
		and the sample solutions).
\end{itemize}
